---
title: "SFResidentialBlockCompare"
author: "Barry Alexander"
date: "7/8/2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Compare Two Residential Housing Blocks within San Francisco, California

Using public data, compare two adjacent residential housing blocks in San Francisco, California.

```{r packages, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
if(!require(readr)) install.packages("readr",repos = "http://cran.us.r-project.org")
if(!require(dplyr)) install.packages("dplyr",repos = "http://cran.us.r-project.org")
if(!require(plotly)) install.packages("plotly",repos = "http://cran.us.r-project.org")

library(readr)
library(dplyr)
library(plotly)
```

Data can be found here: https://data.sfgov.org/Housing-and-Buildings/Land-Use/us3s-fp9q

Click the 'Export' button from the above link to download source data.

```{r load}
# LandUse2016.csv
landUseRaw <- read_csv(file="LandUse2016.csv")
```

## Average square footage per lot for block 6588

```{r square footage 6588}
tidyBlock6588 <- landUseRaw %>%
  filter(BLOCK_NUM == 6588) %>%
  select(everything())

avgSquareFootage6588 <- mean(tidyBlock6588$BLDGSQFT)
print(paste0('Average square footage for block 6588: ',format(round(avgSquareFootage6588, 2), nsmall=2),' ft.'))

```

## Average square footage per lot for block 6583

```{r square footage 6583}
tidyBlock6583 <- landUseRaw %>%
  filter(BLOCK_NUM == 6583) %>%
  select(everything())

avgSquareFootage6583 <- mean(tidyBlock6583$BLDGSQFT)
print(paste0('Average square footage for block 6583: ',format(round(avgSquareFootage6583, 2), nsmall=2),' ft.'))

```

## Use plot.ly to compare histograms of square footage of the residential blocks

```{r plot.ly histogram}
p <- plot_ly(alpha = 0.6) %>%
  add_histogram(x = tidyBlock6588$BLDGSQFT, name="Block 6588") %>%
  add_histogram(x = tidyBlock6583$BLDGSQFT, name="Block 6583") %>%
  layout(barmode = "overlay") %>%
  add_segments(x=avgSquareFootage6588, y=0, xend=avgSquareFootage6588, yend=20, line=list(color="blue", width = 4), name="Mean sqft Block 6588") %>%
  add_segments(x=avgSquareFootage6583, y=0, xend=avgSquareFootage6583, yend=20, line=list(color="orange", width = 4), name="Mean sqft Block 6583")
p
```
generated on: `r as.character(format(Sys.Date(), format="%B %d, %Y"))`